paper1_figures

### 2023-09-11 paper1_markdown.Rmd
11.09
test
test2
final version 11.09

@@

@@

@Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation
@Arora2016: baseline = reciprocity: participants respond with defection to defection and with cooperation to cooperation, but in-group identification can change this --> main effect of identification on cooperation
faced to an in-group defector, high identifiers cooperate more than low (no difference between high and low when the partner cooperates) = compensation + this compensation comes with lower trust toward the partner who defected, so the cooperation is not driven by in-group favoritism
@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)
@VanVugt2009: mention that it happens that high-identifying members compensate for free-riders + when people identify with a social group the are more concerned about their in-group reputation
boost of social identity through inducing competition between groups, but not helpful --> promote a superordinate social identity
group member that strongly identify with their community do not need an economic incentive to cooperate
@Puurtinen2009: between group competition enhances cooperation (even between unrelated individuals) by aligning individual and group interest --> investements in public good higher in the group competition vs normal condition + in the group competition there was more anger toward in-group free-rider and guilt toward its own lack of cooperation --> ingroup identification can be enhanced via intergroup competition
@Noonan2016: study about commons = dog parks --> "having a strong sens of community is related to increased voluntarism" + re-read to see if others parts could be interesting
@Zhang2019: collective risk as operationalization of group identity: (1) cooperation decreased with time when the risk was individual, but not when it was collective; (2) beliefs about others' cooperation formed similarly under the two conditions = these beliefs are interpreted in a different way according to the condition
@Dorrough2015: ingroup favoritism increase with time and it is mediated by expectations of others' contributions + the increment is due to the change between ingroup and outgroup as interaction partners, it is not gradual

@Bardsley2005: paper about conformity (see if it can be useful in this section)

#D

>>>>

+ @Kramer1984: see the phrases underlined in the introduction

@@

@Jackson2012: according to economist, cooperation is an irrational response in social dilemmas (see the articles that he cites)

@@

@Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation
@Arora2016: baseline = reciprocity: participants respond with defection to defection and with cooperation to cooperation, but in-group identification can change this --> main effect of identification on cooperation
faced to an in-group defector, high identifiers cooperate more than low (no difference between high and low when the partner cooperates) = compensation + this compensation comes with lower trust toward the partner who defected, so the cooperation is not driven by in-group favoritism
@VanVugt2009: mention that it happens that high-identifying members compensate for free-riders + when people identify with a social group the are more concerned about their in-group reputation
boost of social identity through inducing competition between groups, but not helpful --> promote a superordinate social identity
group member that strongly identify with their community do not need an economic incentive to cooperate
@Puurtinen2009: between group competition enhances cooperation (even between unrelated individuals) by aligning individual and group interest --> investements in public good higher in the group competition vs normal condition + in the group competition there was more anger toward in-group free-rider and guilt toward its own lack of cooperation --> ingroup identification can be enhanced via intergroup competition
@Noonan2016: study about commons = dog parks --> "having a strong sens of community is related to increased voluntarism" + re-read to see if others parts could be interesting
@Zhang2019: collective risk as operationalization of group identity: (1) cooperation decreased with time when the risk was individual, but not when it was collective; (2) beliefs about others' cooperation formed similarly under the two conditions = these beliefs are interpreted in a different way according to the condition
@Dorrough2015: ingroup favoritism increase with time and it is mediated by expectations of others' contributions + the increment is due to the change between ingroup and outgroup as interaction partners, it is not gradual
@Jackson2011 + @Jackson2012: group performance and group identity on cooperation
@Nockur2020: positive effect of intergroup competition (but not of dispositional competitiveness) on cooperation in social dilemmas
@Kramer1984: a superordinate identity enhances cooperation

@Bardsley2005: paper about conformity (see if it can be useful in this section)   
@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)

#Discussion
